Computing in the Field of Rationals

### 2012-06-29 fields.tex

What is a negative type anyway?

>>>>

Charles Pinter in his book on Abstract Algebra talks about how
negatives were used by \emph{logisticians} of a 1000 years ago used
negative numbers as a ``useful fiction''.  The concept of negative
numbers were ``discovered''much later than fractionals. Like Joan Baez
says ``half an apple is easier to understand than a negative apple''.

Negative types should correspond to sets with negative arity. But what
does that mean? Various approaches have been proposed -- Loeb uses the
notion of multiplicity functions to express negative sized sets
[CITE]. These notions have been extended to Euler characteristic and
Homotopy cardinality of categories by Leinster, Joyal and Schanuel --
negative values are explained sometimes as equalities relating
otherwise independent objects -- Baez tells a story about ``island''
and positive and ``bridges connecting islands'' as negatives (since
the effectively reduce the number of disconnected elements.)

We use the use the syntax {{-b}} for negative types and {{-v}} for
negative values and the axiom {{0 <-> (-b)+b}} as the basis for
negatives. In {{Pi}}/{{PiEE*}}, values flowed from left-to-right in
circuits. Negative types are negative in the sense that they flow in
the opposite direction.
